Scalar on Function Regression

### 2022-01-07 Presentation/slides.tex
Adding

	\begin{frame}{Random Function}
		Random element is a function $X : \Omega \rightarrow \mathcal{S}$ which is defined on a common probability space $(\Omega, \mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a $\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}$
		\begin{itemize}
			\item If $\mathcal{S} = \mathbb{R}$ $\rightarrow$ X is a random variable
			\item If $\mathcal{S} = \mathbb{R}^{n}$ $\rightarrow$ X is a random vector
			\item If $\mathcal{S}$ is a space of functions, $X$ is called a random function
		\end{itemize}
	\end{frame}

	\begin{frame}{Random Function}
		Let $E$ be the index set and this can be described as
		$${\{X(t,\omega) : t \in E, \omega \in \Omega\},}$$
		where $X(t, \cdot)$ is $\mathcal{F}$-measurable function on the sample space $\Omega$\\
		\begin{itemize}
			\item It can be shortened to $X(t)$ by omitting $\omega$
			\item The function is realized when the $X(t)$ have been observed for every $t \in E$
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Stochastic Process Perspective}
		Functional data are the sample curves observed from continuous time stochastic precess\\
		\begin{itemize}
			\item From this perspective, $X(t)$ is a random variable (?)\\
			\item $X(\cdot)$ is a collection of random variables by each time index(?)\\
			\item Realizations of a random function belong in large collection of functions
		\end{itemize}		
	\end{frame}

@@

	\begin{frame}{Plots}
		point plots to link basis expansion
	\end{frame}
	\begin{frame}{Basis Expansion}
		Basis expansion is a linear combination of functions defining a function as described:
		$$X_{i}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad 1\leq i \leq n, \forall t \in E$$
		, where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient
		\begin{itemize}
			\item To make the function smoother
			\item To replace the original scalar data $X_{n}(t_{jn})$ by a smaller collection of $c_{nm}$
		\end{itemize}		
	\end{frame}

	\begin{frame}{Two Typical Types of Basis Function}
		Fourier basis function is written as
		$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\
		\vspace{2\baselineskip}
		B-spline basis function is a flexible curve defined by degree and knots \\
		Each B-spline basis function, $i$-th B-spline basis function of degree $p$, $N_{i,p}(u)$ is defined on Cox-de Boor recursion formula(Do you think I need to put the formula?)
	\end{frame}

>>>>

	\begin{frame}{Random Function}
		Random element is a function $X : \Omega \rightarrow \mathcal{S}$ which is defined on a common probability space $(\Omega, \mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a $\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}.$
		\begin{itemize}
			\item If $\mathcal{S} = \mathbb{R}$ $\rightarrow$ X is a random variable
			\item If $\mathcal{S} = \mathbb{R}^{n}$ $\rightarrow$ X is a random vector
			\item If $\mathcal{S}$ is a space of functions, $X$ is called a random function
		\end{itemize}
	\end{frame}

	\begin{frame}{Random Function}
		Let $E$ be the index set and this can be described as
		$${\{X(t,\omega) : t \in E, \omega \in \Omega\},}$$
		where $X(t, \cdot)$ is $\mathcal{F}$-measurable function on the sample space $\Omega$.\\
		\begin{itemize}
			\item It can be shortened to $X(t)$ by omitting $\omega$
			\item The function is realized when the $X(t)$ have been observed for every $t \in E$
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Square Integrable Function}
		If $f, g \in \mathbb{L}^{2}$,
		$$(ab + bg)(t) = af(t) + bg(t), \quad t \in [0,1] and \forall a,b$$
		, where $a$ and $b$ are scalars. (Maybe don't need)\\
		We can additionally define the inner product as follows:
		$$\langle f,g \rangle = \int_{0}^{1} f(t)g(t)dt$$
		\begin{itemize}
			\item Orthogonolality of two different functions
			\item Distance between functions
		\end{itemize}
	\end{frame}

	\begin{frame}{Stochastic Process Perspective}
		Functional data are the sample curves observed from continuous time stochastic precess.\\
		\begin{itemize}
			\item From this perspective, $X(t)$ is a random variable (?)\\
			\item $X(\cdot)$ is a collection of random variables by each time index(?)\\
			\item Realizations of a random function belong in large collection of functions
		\end{itemize}		
	\end{frame}

@@

	\begin{frame}{Plots}
		point plots to link basis expansion
	\end{frame}
	\begin{frame}{Basis Expansion}
		Basis expansion is a linear combination of functions defining a function as described:
		$$X_{i}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad 1\leq i \leq n, \forall t \in E$$
		, where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient.
		\begin{itemize}
			\item To make the function smoother
			\item To replace the original scalar data $X_{n}(t_{jn})$ by a smaller collection of $c_{nm}$
		\end{itemize}		
	\end{frame}

	\begin{frame}{Two Typical Types of Basis Function}
		Fourier basis function is written as
		$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\
		\vspace{2\baselineskip}
		B-spline basis function is a flexible curve defined by degree and knots. \\
		Each B-spline basis function, $i$-th B-spline basis function of degree $p$, $N_{i,p}(u)$ is defined on Cox-de Boor recursion formula.(Do you think I need to put the formula?)
	\end{frame}
